Algorithm explanation

### 2013-08-22 article/algo.tex

\begin{document}
\maketitle

\section{Algorithm}

@@

We first propose an algorithm to compute a simple solution for the
given $G$ if one exists.  Later we add modifications to the algorithm
for the case that a simple solution does not exist.

Our algorithm works in a constructive manner.
Algorithm~\ref{alg:solveHorn} shows the pseudo-code of our algorithm.

@@

@@

The construction of the algorithm is in two fold.
\begin{itemize}
\item \textbf{Iterative Constraint Building} The process starts from
  generating the weakest constraint that the graph allows and
  iteratively strengthen a constraint until the strongest one.
\item \textbf{Graph Restructuring} If the constraint become
  unsatisfiable during the iteration, restructure the input Horn graph
  to enlarge the solution template.
\end{itemize}
This algorithm enables a solution to be build as simple as possible.

All vertices with predicate variable labels are assigned a simple
template.  For a vertex with a label $P(\mathbf{x})$, the algorithm
assigns a template $\mathbf{a_P} \mathbf{x} + b_P \leq 0$.  Parameters
$\mathbf{a_P}$ and $b_P$ are specified by a linear constraint.

For each predicate variable vertex, build a linear constraint that
parameters in predicate variable templates must satisfy.  The process
is equivalent to generate a linear constraint in interpolation.

$\genConstr$ procedure produces the constraint for all vertices. The
constraints are first built the weakest so that the disjunctiveness of
whole solution template is fixed first.

>>>>

\begin{document}

\section{Horn clause solving}

We propose a new algorithm for solving Horn clauses to generate a
solution which is as simple as possible.  This enables us to obtain
appropriate predicates that are suitable for predicate abstraction in
the program verification techniques.

The construction of the algorithm roughly consists of three parts.
\begin{itemize}
\item \textbf{Horn Graph Building} converts input Horn clauses into a
  \emph{Horn graph} that express the equivalent problem. The process
  also generates a predicate template for every predicate variable
  that the solution will become.  The Horn graph is used throughout
  the algorithm to represent the problem under certain solution
  template.
\item \textbf{Iterative Constraint Generation} is a process to build a
  constraint to compute a solution.  It starts from generating the
  weakest constraint in the sense that the resulting solution would not
  be simple yet.  The process iteratively strengthen a constraint
  until the strongest one while preserving the constraint
  satisfiability. The strongest constraint gives an instanciation of
  templates.
\item \textbf{Graph Restructuring} If the constraint become
  unsatisfiable during the iteration, the process restructure the
  input Horn graph to enlarge the solution template.  This is done by
  considering the unsatisfiable core of the constraint.
\end{itemize}
Our algorithm works in a constructive manner.

Each predicate variable vertex in an input graph has a unique
predicate variable label.  All predicate variables on them are
assigned simple templates.  Those predicate templates are expressed
with template parameters.  Then, according to the graph structure, the
algorithm builds a linear constraint that parameters must satisfy.
For constraint building, the algorithm traverses the input graph in
the topological order on $V_\Rightarrow$, and concatenate the
constraints from predecessors to build the problem constraints.  Each
process to build a constraint on $\mathcal{HC}_v$ for all vertices $v
\in V_\Rightarrow$ is equivalent to generate a linear constraint in
interpolation.

@@

We first propose an algorithm to compute a simple solution for the
given $G$ if one exists.  Later we add modifications to the algorithm
for the case that a simple solution does not exist.  Algorithm~\ref{alg:solveHorn} shows the pseudo-code of our algorithm.

@@

Specifically, for a predicate variable $P(\mathbf{x})$,
the algorithm assigns a template $\mathbf{a}_P \mathbf{x} + b_P \leq
0$.  Parameters $\mathbf{a}_P$ and $b_P$ are specified by a linear
constraint.

@@

$\genConstr$ procedure produces the constraint for a given vertex $v$.

The constraints are first built the weakest so that the disjunctiveness of
whole solution template is fixed first.
